Visualization of [fulle name] Fractional Integrals

### 2019-05-22 fractional/CMJ style files/article-template.tex
almost half-way with edits

\noindent
As was the case for $R_{10}^{\sfrac{4}{5}}$, each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals. The infinitesimals that make up a specific region are translations of that region's right edge. 
The following observations can be made by inspecting Fig.~\ref{fig:geo1}: 
\begin{description}
 \item[Effect of $\alpha$] the grey-tinted solid curves depicted in the different panels of Fig.~\ref{} are not equal to one-another.
 \item[Effect of $t$] the grey-tinted solid curves depicted in each of the panels of Fig.~\ref{} are not translations of one-another. Moreover, the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another.
\end{description}
We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals (i.e. $b_{t}^{\alpha}(y)$) that make up the regions in Fig~\ref{??}. Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig~\ref{??} is larger than the effect that $t$ has on their shape. 
The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their 
sizes are ignored). The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not highly correlated with 
one another).

>>>>

\noindent
As was the case for $R_{10}^{\sfrac{4}{5}}$, Eq.~\eqref{eq:ex1} implies that we can assume that each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals. The infinitesimals that make up a specific region are translations of that region's right edge. 
The following observations can be made by inspecting Fig.~\ref{fig:geo1}: 
\begin{description}
 \item[Effect of $\alpha$] the grey-tinted solid curves depicted in the different panels of Fig.~\ref{} are not equal to one-another.
 \item[Effect of $t$] the grey-tinted solid curves depicted in each of the panels of Fig.~\ref{} are not translations of one-another. Moreover, the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another.
\end{description}
We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals (i.e. the upper limit $b_{t}^{\alpha}(y)$ of Eq.~\eqref{eq:ex1} depends on $\alpha$ and $t$) that make up the regions in Fig~\ref{??}. Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig~\ref{??} is larger than the effect that $t$ has on their shape. 
The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their 
sizes are ignored). The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not highly correlated with 
one another).
